
# Next Steps

## Overview
We have proposed one approach to better represent a modern individual's knowledge by taking the world of unstructured educational content (Youtube videos, Medium articles, etc), classifying it by concepts that belong to one or more subjects from a education-based knowledge graph, and testing a learner's knowledge by generating a set of questions and answers conditioned on the content without the need for the educator to do so. We surveyed some of the relevant machine and deep learning research, introduced Educational Content to Questions and Answers (EC2QA) network, a novel neural network for taking in educational content and generating a set of questions, answers, and an evaluating a learner's knowledge acquisition.

We then proposed to tie these components together as an adaptive knowledge ecosystem consisting of an individual's knowledge footprint, mapped to a knowledge graph, visualised over time as a learner's knowledge journey. This would serve to enable independent (aspiring or current) learner to pursue their life-long self-study. It can also take into consideration the education they acquired from unstructured sources, thereby formalising their informal knowledge.


## Challenges

There will be many challenges in coming up with solutions to enable knowledge acquistion and representation at the learner and group level. We will address some of the primary challenges to pionerring the components of the proposed knowledge ecosystem:                                                        
- Datasets
-- EC2QA dataset
-- Knowledge graph dataset
- Deep Learning Architecture
-- EC2QA network

For our purposes we will focus on the EC2QA network and dataset as the main focus for next steps.

## EC2QA dataset
The success of deep learning techniques are predicated on the assumption that one needs a significant amount of data to train a large neural network to learn the representation that captures the set of admissable functions needed to learn a given concept(s).

The EC2QA network will also face such a challenge and it requires a large dataset of educational content (i.e. Youtube video, Wikipedia or Medium article) along with a set of questions,  which will have a set of correct and incorrect answers for each question.

\[
 \{content1: \{question1: \{answer1, answer2,...\},  question2: \{answer1, answer2,...\},...\},...
\]

This dataset could go through the following process to lower the amount of data needed and utilise the intrinsic structure of educational content.

```{r ec2qa dataset, message=FALSE, warning=FALSE, paged.print=FALSE, echo=FALSE}
library(readr)
library(knitr)
kable(read.csv('img/ec2qa_dataset.csv', check.names = FALSE))

```


1. The network can be trained on unstructured educational content without questions or answers to create an *education embedding* by leveraging unsupervised techniques like variational autoencoder (VAE). This requires a dataset of educational content, possibly many types. This could also be done by a semi-supervised techniques by supervising the media type and learning representations for the types of educational content.


2. The network can then be trained on **existing** educational content that already has preexisting questions and answers for each part of the content (i.e. Khan Academy, Udacity, Coursera). The domain of structured educational content is in fact very different from the unstructured content and may hinder the network but we believe it might be the case that it helps. This is worth experimenting with.


3. The final step is annotating a set of unstructured educational content with questions and answers.


## Education Partners
The second step above requires a large amount of educational content paired with question and answer sets. This data is rich and informative and could help map the unstructured representations. Most of these sets have been created by experts and educators and their efforts could be valuable for our model to learn from. For this purpose, we would need to partner with large educational institutions (i.e. Udacity, Coursera, MOOCs, Edx, Khan Academy) to work with their datasets and also collaborate on how we annotate the space of unstructured educational content.

## Educator Enrichment
The third and final dataset that would be used as our primary data source to train and test the model's performance, remains the most important component as well as being the most time and labour intensive. Partnering with educators and subject matter experts to source the subspace of unstructured educational content and to create questions and answers, we would eventually arrive at a curated dataset that our model needed to learn and generalize from.

## Minimum Viable Dataset

We propose to narrow the problem space and jumpstart research in this area by focusing on only one subject (i.e. psychology, mathematics, or design) rather than to try to take on mapping the whole space of unstructured educational content. This drastically reduces the data that is needed and the number of experts and partners needed to kickstart the initiative.


## Call for collaborators

We hope to bring together collaborators that would include machine learning researchers, educators, technologists, and designers to begin our first foray into a modern knowledge ecosystem. Specifically starting with the EC2QA dataset and network, one education subject, and an educational partner.

Please email us at [two@dyadxmachina.com](two@dyadxmachina.com) with the subject *Knowledge Graph Initiative* or leave your email below.

```{r echo=FALSE, results="asis"}
library(readr)
cat( paste( readLines( "mailchimp.html" , warn = FALSE) ) )
```

## Conclusion

In conclusion, we presented a new perspective on knowledge acquistion and representation, and proposed an ecosystem that would support a modern and adaptative knowledge ecosystem that a learner can use and rely on for their entire life-time.

Our main task was to take an individual and begin to get a true depiction of their knowledge beyond their traditional degree which is only a small percentage of someone's education. We focused on taking the world of unstructured educational content online, and how to provide structure in the form of testing and mapping it to a knowledge graph.

There is still much more research to be done in bringing to life the Educational Content to Questions and Answers (EC2QA) neural networks as well as the data needed for training and the collaboration required amongst machine learning researchers, teachers, and designers,

As deep learning researchers, we are looking forward to designing or seeing others design the minimum viable dataset and architecture motivate by this work.

# About Authors

## Haohan Wang
## Fanli Zheng (Christian Ramsey)
## Contact
Feel Free to contact us if you have any question:


Visit our website [dyadxmachina.com](dyadxmachina.com)

Haohan Wang: haohan723@gmail.com

Christian Fanli Ramsey: thechristianramsey@gmail.com
